High-level cognition is supported by information-rich but compressible brain activity patterns

### 2023-12-24 paper/main.tex
backing up network shuffling (permutation) analyses

If the informativeness and compressibility of brain activity patterns vary over
time, do these properties might also vary across brain networks? We used a
network parcellation identified by \cite{YeoEtal11} to segment the brain into
seven distinct networks. The networks can be sorted (roughly) in order from
lower-level to higher-level cortex as follows (Figs.~\ref{fig:networks}A--C):
visual, somatomotor, dorsal attention, ventral attention, limbic,
frontoparietal, and default mode. Next, we computed decoding curves separately
for the activity patterns within each network and identified each network's
inflection point, for each experimental condition. Moving from low-order
networks to higher-order networks, we found that decoding accuracy tended to
increase in the higher-level experimental conditions and decrease (slightly) in
the lower-level experimental conditions (Fig.~\ref{fig:networks}D, E;
Spearman's rank correlation between decoding accuracy and network order:
intact: $\rho = 0.362, p < 0.001$; paragraph: $\rho = 0.441, p < 0.001$; word:
$\rho = -0.102, p = 0.007$; rest: $\rho = -0.354, p < 0.001$). This suggests
that higher-order networks may carry more content-relevant or stimulus-driven
``information.'' We found no clear trends in the proportions of components
required to achieve 5\% decoding accuracy across networks or conditions
(Fig.~\ref{fig:networks}F). We note that the limbic network we considered here
often overlaps with low (imaging) signal regions, and therefore it may be
difficult to draw strong conclusions about this network's informativeness or
compressibility.

>>>>

If the informativeness and compressibility of brain activity patterns vary over
time, do these properties might also vary across brain networks? We used a
network parcellation identified by \cite{YeoEtal11} to segment the brain into
seven distinct networks. The networks can be sorted (roughly) in order from
lower-level to higher-level cortex as follows (Figs.~\ref{fig:networks}A--C):
visual, somatomotor, dorsal attention, ventral attention, limbic,
frontoparietal, and default mode. Next, we computed decoding curves separately
for the activity patterns within each network and identified each network's
inflection point, for each experimental condition. Moving from low-order
networks to higher-order networks, we found that decoding accuracy tended to
increase in the higher-level experimental conditions and decrease (slightly) in
the lower-level experimental conditions (Fig.~\ref{fig:networks}D, E;
Spearman's rank correlation between decoding accuracy and network order:
intact: $\rho = 0.362, p < 0.001$; paragraph: $\rho = 0.441, p < 0.001$; word:
$\rho = -0.102, p = 0.007$; rest: $\rho = -0.354, p < 0.001$). This suggests
that higher-order networks may carry more content-relevant or stimulus-driven
``information.'' We found no clear trends in the proportions of components
required to achieve 5\% decoding accuracy across networks or conditions
(Fig.~\ref{fig:networks}F). We note that the limbic network we considered here
often overlaps with low (imaging) signal regions, and therefore it may be
difficult to draw strong conclusions about this network's informativeness or
compressibility. We also considered the possibility that the correlations with
network order might be influenced by the numbers of nodes in each network. We
designed a permutation-based procedure to address this possibility, whereby we
repeated the above analyses using shuffled network labels (see \textit{Network
permutation tests}).  The correlations between decoding accuracy and network
order... <INSERT RESULTS>
